Ceph Parallel File System Evaluation Report

### 2013-08-20 ceph-eval.tex
Incoporate Sarp's changes on 1-7.

\setmainfont{rosario}
\setmonofont{Consolas}
%\setmainfont{Times}
%\setmonofont{Inconsolata}
%\setmonofont[Scale=0.8]{Monaco}
%\setmonofont[Scale=0.8]{Courier}

\title{Ceph Parallel File System Evaluation Report}
\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}

@@

NCCS contracted Inktank, the major developer behind the open-source parallel
file system, Ceph, for a deep-dive study. It covers a wide range of technical
topics from system setup, deployment, administration to \hl{internal mechanisms}. In
comparison to other parallel file systems, Ceph has a number of distinctive
features:

\begin{itemize}
  \item Ceph has an intelligent and powerful data placement mechanism, known as
  CRUSH. The CRUSH algorithm allows a client to pre-calculate layout
  information while taking into consideration failure domains and hierarchical storage tiers.

@@

\item Ceph's design assumes that the system is composed of
unreliable components; fault-detection and fault-tolerance (e.g., replication) are
the norm rather than the exception. This is in line with the expectations of
exascale computing.

\item Ceph is built on top of a unified object management layer,
\texttt{RADOS}. Both metadata and the actual data can take advantage of this
uniformity.

\item Most of the Ceph processes reside in user-space. Generally speaking, this makes the
system easier to debug and maintain. The client-side support has long been
integrated into Linux mainline kernel, which make the deployment and out-of-box
experience easier.

@@

As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
system evaluation. The goal is to investigate the feasibility of using the Ceph system as
a candidate for our next-generation HPC storage solution.
This report presents our experience, results, and observations. While evaluating
our results, please keep in mind that Ceph is such a moving target that its
code base is changing rapidly. In between releases, we often experienced different
outcomes. We will try to make clear in the report when such changes occurred.

@@

We used Data Direct Networks' (DDN) SFA10K as the storage backend during this evaluation. It consists of
200 SAS drives and 280 SATA drives driven by four hosts. Each host has two InfiniBand (IB) QDR
connections to the storage backend. We configured and used four Mellanox IB cards as the
primary connections, which by calculation can saturate the controller's maximum theoretical
throughput (11-12 GB/s). The connection diagram is illustrated below:`

\begin{figure}[htb]
\centering
\includegraphics[width=4in]{figs/sfa10k}
\caption{DDN SFA10K Hardware Diagram}
\end{figure}

The supporting infrastructure nodes are summarized in the following table:

@@

    \end{tabular}

\end{table}

The hosts ran Redhat 6.3 with kernel version 3.5.1 (rhl-ceph image), Glibc 2.12
with syncfs support, locally patched. We used the Ceph 0.55 release in the
initial tests, then upgraded to 0.64 and then to 0.67RC for second round of tests. For a
complete a list of hosts that are running ceph images, one can execute:

\begin{Verbatim}
$ grep "rhel6-ceph" /etc/gedi/MAC.info
\end{Verbatim}

\section{Baseline Performance}

\subsection*{Block I/O}
We first establish baseline performance by measuring block I/O performance.
At the block level, with each LUN configured with RAID6 8+2, we have the following
results:

\begin{table}[htb]
\centering
\begin{tabular}{ll}
    \toprule
    SAS single LUN sequential read & ~1.4 GB/s \\
    SATA single LUN sequential read & ~955 MB/s \\[0.5em]
    Single host with four SAS LUNs & ~ 2.8 GB/s \\
    Single host with seven SATA LUNs & ~ 2.6 GB/s \\
    \bottomrule
\end{tabular}

\end{table}

Single host refers to one of four tick-oss nodes, which drives the entire system.
Overall, the entire system can perform at 11 GB/s, compared to its
theoretical maximum of 12 GB/s.

\subsection*{IP over IB}

Note that Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
Because our testbed has IB, we used IP over IB (IPoIB) for networking\footnote{Inktank is 
investigating using rsockets to improve performance when using an IB fabric}.
A pair of hosts connected by IB QDR using IPoIB can transfer data at 2.7 GB/s if the
hosts are tuned per recommendations from Mellanox. With all four hosts (OSD servers), we would expect
the aggregate throughput to be in the neighborhood of 10 GB/s.

Unfortunately there was not enough time to do more detailed analysis of the network
performance. Later, we will see RADOS is performing a
maximum of 5-6 GB/s driven by four hosts.  So, this test shows that we
have enough network bandwidth (i.e., IP over IB is not a bottleneck in this
case).

\section{The Starting Point of System Tuning}

Base upon past experience and further experimentation, we started out with the
following set of tuning parameters:

\begin{table}[htb]
\centering
\begin{tabular}{ll}
    \toprule
    \verb!nr_requests! & 2048 \\
    \verb!read_ahead_kb! & 4096 \\
    \verb!scheduler! & deadline \\
    \bottomrule
\end{tabular}

\end{table}

\section{XFS Performance}

Ceph supports multiple backend file systems including btrfs, ext4, and xfs.
Due to its performance and maturity, we chose to use XFS. We
experimented with XFS to acquire a set of sensible configuration parameters
which hopefully provided optimal performance for the SFA10K. We sampled a selected set of parameters (block size,
queue depth, request size, sequential read and write). We settled on the following
configuration: mount with \verb!nobarrier,noatim,inode64! options.
The \verb!inode64! option had a notable improvement on sequential write (around
20\%).

%% Can the graphs be adjusted to have the same values in the Y axis?
\begin{figure}[htb]
\centering
%% -- 1st figure
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/xdd-read}
\caption{XFS read scaling on \# of devices}
\label{fig:xfs-read}
\end{minipage}%
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/xdd-write}
\caption{XFS write scaling on \# of devices}
\label{fig:xfs-write}
\end{minipage}%
\end{figure}

%% Are the read and write graphs wrong or should the second sentence below be about write
%% instead of read?
The read and write results are summarized in Figures~\ref{fig:xfs-read}
and~\ref{fig:xfs-write}, respectively. These show scaling behavior over the number of devices, which
indicates that XFS can get to the peak write performance with five SATA LUNs,
then there is a bit of degradation from there. Changes to
the queue depth do not seem to make any obvious difference in the performance.

@@

RADOS is the Ceph object store, a foundational component for CephFS file
system. There are three types of scaling tests we are interested at the RADOS layer:

\begin{itemize}
  \item scaling on the number of servers
  \item scaling on the number of clients
  \item scaling on the number of OSDs
\end{itemize}

Our system setup poses some limitations on the scalability tests we want to
perform. In particular, we currently have four OSS servers, eight clients, and eleven OSD servers
per client. The scaling tests will be within these constraints.

We use the open-source tool RADOS Bench, developed by Inktank, to perform our
initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
writes out objects to the underlying object storage as fast as possible, and
then later reads those objects in the same order as they were written.

We have observed that using two or more client processes and many concurrent
operations are important when performing these tests.  We tested eight client processes 
with 32 concurrent 4 MB objects in flight each. We created a pool for
each RADOS Bench process to ensure that object reads come from independent pools
(RADOS Bench is not smart enough to ensure that objects are not read by multiple
processes and thus possibly cached).  A sync and flush is performed on every
node before every test to ensure no data or metadata is in cache.  All tests
were run with replication set to one.  Only XFS was present
and usable for the underlying OSDs, so BTRFS and EXT4 file systems were not
tested at this time.

\subsection{Scaling on number of OSDs}

In the following test, a single Ceph host drives $n$ OSDs, where $n$
increases from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
We ran the test against a single client with four concurrent processes. In this test
case, we observe that the OSS exhibits near linear scalability up to nine
OSDs, and is still trending upwards at eleven OSDs. This suggests that we have not reached the
saturation point yet. Additional testing would require provisioning more OSDs on the SFA10K backend.

\begin{figure}[H]
\centering
%% -- 1st figure
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/rados_osd}
\caption{RADOS scaling on \# of OSDs}
\label{fig:osd-scale}
\end{minipage}%
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/rados_server}
\caption{RADOS scaling on \# of servers}
\label{fig:oss-scale}
\end{minipage}%
\end{figure}

\subsection{Scaling on number of servers}

In this test, we exercise OSS numbers from one to four, driven by four clients with four
concurrent process for each client. Each additional OSS adds eleven more OSDs into
play. We observe that Ceph exhibits linear scaling with regard to
number of servers as well, at least in the given set of servers. However, the peak
performance we are seeing is about the half of what are expecting from the SFA10K.
For writes, it is attributed to the way Ceph performs
journaling: Ceph does not support meta-data only journaling, therefore every
write is the equivalent of a double-write: once to the data device, once to the
journaling device. This effectively cuts the system bandwidth in half. That said,
it does not explain the read performance -- it is better than write, but 
still far from the theoretical maximum.

@@

We used the synthetic IOR benchmark suite the for file system level test. The particular
parameter setup is show in Table \ref{tbl:ior}. Each client node has 6 GB of
physical memory, the block size is set so as to mitigate cache effects. In
addition, the test harness program will issue the following commands at the
beginning of each test:

@@

The full permutation of IOR parameters were not explored due to I/O errors we encountered.
We were, however, able to record results in two extreme cases as far as
transfer size is concerned: 4 KB and 4 MB, using the same number of OSS servers
(4) and same block size (8 GB), the results are illustrated in Figure
\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:

@@

\begin{figure}[H]
\centering
%% -- 1st figure
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/ior_4k}
\caption{IOR tests: 4k transfer size}
\label{fig:ior4k}
\end{minipage}%
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/ior_4m}
\caption{IOR tests: 4m transfer size}
\label{fig:ior4m}
\end{minipage}%
\end{figure}

\begin{itemize}
  \item The small read performance is almost an anomaly -- we need to
  investigate why it is so low compare to write performance.
  \item The large read performance is almost half of the write performance,
  which is the opposite of the RADOS-level results. 
  \item The write performance is half of what we can obtain from
  RADOS Bench. When number of clients reaches 8, there is a significant
  performance drop as well. 
\end{itemize}

@@

After the initial test results, we tried various combinations of tweaks
including changing the number of filestore op threads, putting all
of the journals on the same disks as the data, doubling the OSD count, and
upgrading Ceph to a development version which reduces the seek overhead caused
by \texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are
now included as of the Ceph Cuttlefish release).  The two biggest improvements
resulted from disabling CRC32c checksums and increasing the OSD count on the
server.  With these changes, we are seeing better results.

@@

Despite the excellent write throughput we saw during the individual server
tests, throughput did not scale.  We spent a significant amount of time
investigating this phenomenon. Ultimately, we were able to replicate this finding
when running concurrent disk throughput tests directly on the servers without
Ceph involved. The second RAID processor on each DDN controller would max out when
three or more LUNs were written concurrently. It turns out the root of the problem
was a regression on DDN firmware update -- in particular, the cache
mirroring was not behaving as it should.\footnote{DDN recently released a new
firmware version and we were told the issue has been fixed. Unfortunately, we didn't get
a chance to verify it during our test cycle.}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=5in]{rados-064-oss}
\caption{RADOS Bench Scaling on \# of Server, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
\label{fig:rados-064-oss}
\end{figure}

\section{Improving Ceph File System Performance}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=4in]{ior-client-no-crc32}
\caption{IOR test with no client-side CRC32}
\label{fig:ior-no-client-crc32}
\end{figure}

@@

\begin{figure}[htb]
\centering
%% -- 1st figure
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/mdtest-fcreate}
\caption{file creation vs.  \# of clients}
\label{fig:mdtest-fcreate}
\end{minipage}%
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/mdtest-dcreate}
\caption{directory creation vs. \# of clients}
\label{fig:mdtest-dcreate}
\end{minipage}%
\end{figure}

>>>>

\setmainfont{rosario}
%\setmonofont{Consolas}
%\setmainfont{Times}
\setmonofont{Inconsolata}
%\setmonofont[Scale=0.8]{Monaco}
%\setmonofont{Courier}

%\title{Ceph Parallel File System Evaluation Report}
%\author{Feiyi Wang, Sarp Oral, Doug Fuller, Blake Caldwell, James Simmons\\
%Brad Settlemyer, Scott Atchley, Jason Hill, Mark Nelson}

@@

National Center for Computational Sciences (NCCS), in collaboration with
Inktank Inc, has prepared a detailed performance and scalability study of
Ceph file system. Ceph is originated from Sage Weil's PhD research
at UC Santa Cruz around 2007 and it is designed to be a reliable, scalable
fault-tolerant parallel file system. Inktank is now the major developer behind
the open-source parallel file system to sheperd its development and provide
commerical support.

In comparison to other parallel file systems, Ceph has a number of distinctive
features:

\item Ceph has an intelligent and powerful data placement mechanism, known as
  CRUSH. The CRUSH algorithm allows a client to pre-calculate object
  placement and layout while taking into consideration failure domains and
  hierarchical storage tiers.

@@

\item Ceph's design assumes that the system is composed of
unreliable components; fault-detection and fault-tolerance (e.g., replication) are
the norm rather than the exception. This is in line with the expectations of
Exascale computing.

\item Ceph is built on top of a unified object management layer,
\texttt{RADOS}. Both metadata and the file data can take advantage of this
uniformity.

\item Most of the Ceph processes reside in user-space. Generally speaking, this makes the
system easier to debug and maintain. The client-side support has long been
integrated into Linux mainline kernel, which eases the deployment and out-of-box
experience.

@@

As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
file system evaluation. The goal of our study is to investigate the feasibility
of using the Ceph for our future HPC storage deployment.
This report presents our experience, results, and observations. While evaluating
our results, please keep in mind that Ceph has not matured yet for scientific
HPC community that its code base is changing rapidly. In between releases, we
often experienced different outcomes. We will try to make clear in the report
when such changes occurred.

@@

We used Data Direct Networks' (DDN) SFA10K as the storage backend during this
evaluation. It consists of 200 SAS drives and 280 SATA drives, organized into
various RAID levels by two active-active RAID controllers. The exported RAID
groups by these controllers are driven by four hosts.
Each host has two InfiniBand (IB) QDR connections to the storage backend.
We used a single dualport Mellanox connectX IB card per host.
By our calculation, this setup can saturate SFA10K's maximum theoretical
throughput (\textasciitilde 12 GB/s). The connection diagram is illustrated in
Figure~\ref{fig:ddn-sfa10k}.

\begin{figure}[htb]
\centering
\includegraphics[width=4in]{figs/sfa10k}
\caption{DDN SFA10K Hardware and Host Connection Diagram}
\label{fig:ddn-sfa10k}
\end{figure}

Our Ceph testbed employs a collection of testing nodes. These nodes and their
roles are summarized in Table~\ref{tbl:ceph-test-nodes}. In the following
discussion, we use ``servers'', ``osd servers'', ``server hosts''
interchangably. We will emphasize with ``client'' prefix when we want to
distinguish it from above.

@@

    \end{tabular}
\caption{Support nodes involved in Ceph testbed}
\label{tbl:ceph-test-nodes}
\end{table}

All hosts  (client and servers) were configured with Redhat 6.3 and kernel
version 3.5.1 (rhl-ceph image), Glibc 2.12 with syncfs support, locally patched.
We used the Ceph 0.55 release in the initial tests, upgraded to 0.64 and then to
0.67RC for a final round of tests.

%For a complete a list of hosts that are running ceph images, one can execute:

%\begin{Verbatim}
%$ grep "rhel6-ceph" /etc/gedi/MAC.info
%\end{Verbatim}

\section{Baseline Performance}
\label{sec:block-io}

\subsection{Block I/O over Native IB}
We first established baseline performance by measuring observed block I/O
performance.
At the block-level, with each LUN configured as a RAID6 8+2 array, we had the
following results as shown in Table~\ref{tbl:block-io-baseline}.

\begin{table}[htb]
\centering
\begin{tabular}{ll}
    \toprule
    SAS single LUN sequential read & ~1.4 GB/s \\
    SATA single LUN sequential read & ~955 MB/s \\[0.5em]
    Single host with four SAS LUNs & ~ 2.8 GB/s \\
    Single host with seven SATA LUNs & ~ 2.6 GB/s \\
    \bottomrule
\end{tabular}
\caption{Block I/O performances on single LUN and single host}
\label{tbl:block-io-baseline}
\end{table}

Single host in this table refers to one of four tick-oss nodes. Four tick-oss
nodes drive the SFA10K backend storage. Overall, we observe that the entire
system can perform at 11 GB/s, compared to DDN SFA10K's theoretical maximum of
12 GB/s.

\subsection{IP over IB}

Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
Because our entire testbed is IB-switched, we used IP over IB (IPoIB) for
networking\footnote{As of writing of this report, Inktank is investigating using
rsockets to improve performance with IB fabric}. Through simple
\verb!netperf! tests, we observed that a pair of hosts connected by IB QDR using
IPoIB can transfer data at 2.7 GB/s (the hosts are tuned per recommendations
from Mellanox). With all four hosts (OSD servers), we expect the aggregate
throughput to be in the neighborhood of 10 GB/s.

Unfortunately there was not enough time to do more detailed analysis of the network
performance. Later, we will see RADOS is performing a
maximum of 5-6 GB/s driven by four hosts.  So, it shows that we
have enough network bandwidth (i.e., IP over IB is not a bottleneck in this
case).

\section{System Tuning}

Base upon past experience and further experimentation, we started out with the
following set of tuning parameters on OSD servers:

\begin{table}[htb]
\centering
\begin{tabular}{ll}
    \toprule
    \verb!nr_requests! & 2048 \\
    \verb!read_ahead_kb! & 4096 \\
    \verb!scheduler! & deadline \\
    \bottomrule
\end{tabular}
\caption{System tuning parameters}
\end{table}

\section{XFS Performance As Backend File System}

Ceph supports multiple backend file systems including Btrfs, Ext4, and XFS.
Due to its performance and maturity, we chose XFS. We experimented with XFS to
acquire a set of configuration parameters which provided optimal performance for
the SFA10K. We sampled a selected set of parameters (block size, queue depth,
request size, sequential read and write). We settled on the following
configuration: mount with \verb!nobarrier,noatim,inode64! options.
The \verb!inode64! option had a notable improvement on sequential write (around
20\%).

%% Can the graphs be adjusted to have the same values in the Y axis?
\begin{figure}[htb]
\centering
%% -- 1st figure
\centering
\includegraphics[width=3in]{data/xdd-read}
\caption{XFS read performance scaling on number of devices}
\label{fig:xfs-read}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=3in]{data/xdd-write}
\caption{XFS write performance scaling on number of devices}
\label{fig:xfs-write}
\end{figure}

%\begin{figure}[htb]
%\centering
%% -- 1st figure
%\begin{minipage}[t]{0.5\linewidth}
%\centering
%\includegraphics[width=3in]{data/xdd-read}
%\caption{XFS read performance scaling on number of devices}
%\label{fig:xfs-read}
%\end{minipage}%
%\begin{minipage}[t]{0.5\linewidth}
%\centering
%\includegraphics[width=3in]{data/xdd-write}
%\caption{XFS write performance scaling on number of devices}
%\label{fig:xfs-write}
%\end{minipage}%
%\end{figure}

% % Are the read and write graphs wrong or should the second sentence below be
% about write % instead of read?
The read and write performance results are summarized in
Figures~\ref{fig:xfs-read} and~\ref{fig:xfs-write}, respectively. These show
scaling behavior over the number of LUNs, which indicates that XFS can reach
the peak write performance with five SATA LUNs. Increasing number of LUNs
beyond 5, degradation happened. 
Changes to the queue depth was not observed to make any obvious difference in
the performance. For these tests, we used the \verb!xdd! benchmark with direct
I/O and a request size of 32 KB.

@@

RADOS is the Ceph object store, the foundational component for CephFS file
system. There are two types of scaling tests we are interested at the RADOS
layer:

\begin{itemize}
  \item scaling on the number of OSD servers
  \item scaling on the number of OSDs per OSD server
\end{itemize}

Our system setup poses some limitations on the scalability tests we wanted to
perform. In particular, we currently had four OSD servers, eight clients, and
eleven OSD servers per client. The scaling tests, therefore, will be within
these constraints.

We used the open-source RADOS Bench tool, developed by Inktank, to perform our
initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
writes out objects to the underlying object storage as fast as possible, and
then later reads those objects in the same order as they were written.

We observed that using two or more client processes and many concurrent
operations are important when performing these tests.  We tested eight client processes 
with 32 concurrent 4 MB objects in flight each. We created a pool for
each RADOS Bench process to ensure that object reads come from independent pools
(RADOS Bench is not smart enough to ensure that objects are not read by multiple
processes and thus possibly cached).  A sync and flush is performed on every
node before every test to ensure no data or metadata is in cache.  All tests
were run with replication set to one.  The backend file systems were XFS,
BTRFS and EXT4 file systems were not tested at this time.

\subsection{Scaling on number of OSDs per server}

In the following test, a single Ceph host drives $n$ OSDs, where $n$ increases
from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
We ran the test against a single client with four concurrent processes. In this
test case, we observe that the OSD server exhibits near linear scalability up to
nine OSDs, and is still trending upwards at eleven OSDs. This suggests that we
have not reached the saturation point yet. Additional testing would require
provisioning more OSDs on the SFA10K backend.

\begin{figure}[H]
\centering
%% -- 1st figure
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/rados_osd}
\caption{RADOS scaling on number of OSDs}
\label{fig:osd-scale}
\end{minipage}%
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/rados_server}
\caption{RADOS scaling on number of servers}
\label{fig:oss-scale}
\end{minipage}%
\end{figure}

\subsection{Scaling on number of OSD servers}

In this test, we exercise OSD servers from one to four, driven by four hosts
each with four RADOS Bench process. Each additional OSD server
adds eleven more OSDs into play. We observe that Ceph exhibits linear scaling with
regard to number of servers as well, at least in the given set of servers.
However, the peak performance we are seeing is about the half of what are
expecting from the SFA10K (compare to the baseline block I/O perforamnce number
presented in Section~\ref{sec:block-io}).

For writes, the lost performance is attributed to the way Ceph performs
journaling:
Ceph does not support meta-data only journaling, therefore every write is the
equivalent of a double-write: once to the data device, once to the journaling
device. This effectively cuts the observed system bandwidth in half. That said,
it does not explain the read performance -- it is a little better than write,
but still far from the theoretical maximum.

@@

We used the synthetic IOR benchmark suite for file system level performance and
scalability test.
The particular parameter setup is show in Table \ref{tbl:ior}. Each client node
has 6 GB of physical memory, the block size is set so as to mitigate cache
effects. In addition, the test harness program issues the following commands
at the beginning of each test:

@@

The full permutation of IOR parameters were not explored due to I/O errors we encountered.
We were, however, able to record results in two extreme cases as far as
transfer size is concerned: 4 KB and 4 MB, using a fixed number of OSD servers
(4) and fixed block size (8 GB), the results are illustrated in Figure
\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:

@@

\begin{figure}[H]
\centering
%% -- 1st figure
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/ior_4k}
\caption{IOR tests: 4 KB transfer size}
\label{fig:ior4k}
\end{minipage}%
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/ior_4m}
\caption{IOR tests: 4 MB transfer size}
\label{fig:ior4m}
\end{minipage}%
\end{figure}

\begin{itemize}
  \item The small read (4 KB transfer size) performance is almost an anomaly --
  we will investigate why it is so low compare to write performance and improved
  results in Section~\ref{sec:improve-ior}.
  \item The large read (4 MB transfer size) performance is almost half of the
  RADOS read performance.

  \item The write performance is also about half of what we can obtain from
  RADOS Bench. When number of clients reaches 8, there is a significant
  performance drop as well. 
\end{itemize}

@@

After the initial test results, we tried various combinations of tweaks
including changing the number of filestore op threads, putting all of the
journals on the same disks as the data, doubling the OSD count, and upgrading
Ceph to a development version which reduces the seek overhead caused by
\texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are now
included as of the Ceph Cuttlefish release, v0.61).  The two biggest
improvements resulted from disabling CRC32c checksums and increasing the OSD
count on the server.  With these changes, we are seeing better results.

@@

During a second round of test performed by Inktank, we noticed a dramatic drop
on RADOS performance: even though write throughput on individual server met the
expectation, it did not scale across servers.

We spent a significant amount of time
investigating this phenomenon. Ultimately, we were able to replicate this finding
when running concurrent disk throughput tests directly on the servers without
Ceph involved. The second RAID processor on each DDN controller would max out when
three or more LUNs were written concurrently. It turns out the root of the problem
was a regression on DDN firmware update -- in particular, the cache
mirroring was not behaving as it should.\footnote{DDN recently released a new
firmware version and we were told the issue has been fixed. Unfortunately, we didn't get
a chance to verify it during our test cycle.}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=5in]{rados-064-oss}
\caption{RADOS Bench Scaling on number of servers, Ceph 0.64, 4 MB I/O, 8 client
nodes}
\label{fig:rados-064-oss}
\end{figure}

\section{Improving Ceph File System Performance}
\label{sec:improve-ior}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=4in]{ior-client-no-crc32}
\caption{IOR test with disabling client-side CRC32}
\label{fig:ior-no-client-crc32}
\end{figure}

@@

\begin{figure}[htb]
\centering
%% -- 1st figure
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/mdtest-fcreate}
\caption{File creation vs.  number of clients}
\label{fig:mdtest-fcreate}
\end{minipage}%
\begin{minipage}[t]{0.5\linewidth}
\centering
\includegraphics[width=3in]{data/mdtest-dcreate}
\caption{Directory creation vs. number of clients}
\label{fig:mdtest-dcreate}
\end{minipage}%
\end{figure}
